\vfill A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications

### 2014-05-16 Paper/paper.tex
Implementation edits

\subsubsection{Mocha with Chai.js}
Our choice of using Mocha with Chai.js was made because Mocha offers the flexibility of choosing one's own assertion library while still being structured in a way that all developers can read the code.

@@

Quite frankly, we didn't have the time or interest in setting up our own Jenkins server. Given enough resources and time, Jenkins will surely beat all of the rest of the CI frameworks, however, there's something to be said for ease of setup and total time to first interaction with the tool.

@@

Overall, the CI frameworks were all impressive and usable. The main driving factor was simply that we didn't have our application on any of the more common repositories and at the time of this writing our application was closed-source. We have every intention of opening it to the public as soon as we get a version that is polished.

>>>>

\subsubsection{Mocha with Chai.js}
Our choice of using Mocha with Chai.js was made because Mocha offers the flexibility of choosing one's own assertion library and testing interface while still having a default structure that all developers can read and code.

@@

Quite frankly, we did not have the time nor interest in setting up our own Jenkins server. Given enough resources and time, Jenkins will surely beat all of the rest of the CI frameworks. However, there's something to be said for ease of setup and total time to first use of a tool.

@@

Overall, the CI frameworks were all impressive and usable. The main driving factor was simply that we didn't have our application on any of the more common repositories and at the time of this writing our application was closed-source. We have every intention of opening it to the public as soon as we get a version that is more polished.
